---
title: "ASD_ACE"
author: "Zoë Hawks"
date: "11/9/2017"
output: pdf_document
---

##Setting up dataframe
```{r, warning = FALSE, message = FALSE}
library(lavaan)
library(semPlot)
library(tidyverse)
library(dplyr)
library(forcats)

setwd("/Users/zashawks/Desktop/Stats/Longitudinal/ALDA")
mydata <- read.csv("ASD_master_data_stats.csv", header=TRUE)  

mydata_wide <- mydata %>% 
  select(famid, Random_twin_assignment, zy_final_all, sci, rrb, rrb_30_36, sci_30_36) %>%
  rename("sci36" = "sci_30_36", "rrb36" = "rrb_30_36") %>%
  filter(!is.na(Random_twin_assignment), zy_final_all == 1 | zy_final_all == 2 | zy_final_all == 5) %>%
  mutate(zy_final_all = ifelse((zy_final_all == 5 | zy_final_all == 2), 2, 1)) %>%
  mutate_at(c("zy_final_all"), funs(as.factor(.))) %>%
  mutate(zy_final_all = factor(zy_final_all, labels = c("MZ", "DZ"))) %>%
  mutate_at(c("sci", "rrb", "rrb36", "sci36"), funs(as.numeric(.))) %>%
  gather(-(famid:zy_final_all), key = "variable", value = "value") %>%
  unite(varT, variable, Random_twin_assignment) %>%
  spread(key = varT, value = value)
```

##Hypotheses  

Given previous evidence in children indicating that autistic traits are highly heritable, we predict heritability on the order of roughly 80-90% for our social communicative factor (SCI). However, it is unclear (1) whether genetic effects will be this large in infancy and (2) how this effect may change over the course of early development (i.e., 18 to 36 months).  
  
Some background on biometric models:  
* A = additive effects stemming from shared genetic material (MZ share 100%, DZ share 50%)  
* D = non-additive effects (e.g., dominance effects; MZ = share both alleles at 100% of loci, DZ = share both alleles at *25%* of loci)  
* C = shared environmental effects (e.g., prenatal, shared home)  
* E = non-shared environment (e.g., different peer groups, attending different schools)  
* Common to test different models based on hypotheses about genetic and environmental structure of construct -- ACE, ADE, CE, AE  

##Descriptives
```{r}
#TBC...
```

##RRB @ 18 months  
```{r, warning = FALSE, message = F}
#ACE model
ACE_18 <-'

# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*rrb_0 + c(a,a)*rrb_0
  A2=~ NA*rrb_1 + c(a,a)*rrb_1 
  C =~ NA*rrb_0 + NA*rrb_1 + c(c,c)*rrb_0 + c(c,c)*rrb_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  C ~~ 1*C
  rrb_0~~c(e,e)*rrb_0
  rrb_1~~c(e,e)*rrb_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  C ~~ 0*A1 + 0*A2
'
ACE_18.fit <- cfa(ACE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
semPaths(ACE_18.fit)
semPaths(ACE_18.fit, what = "std")

#ADE model

#CE model

#AE model

#Model comparisons

##Summarizing fit for preferred model
summary(ACE_18.fit)
fitMeasures(ACE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))

#Calculating heritability for preferred model
estA <- as_tibble(parameterEstimates(ACE_18.fit)) %>% 
  filter(label == "a") %>% 
  select(est)
estC <- as_tibble(parameterEstimates(ACE_18.fit)) %>% 
  filter(label == "c") %>% 
  select(est)
estE <- as_tibble(parameterEstimates(ACE_18.fit)) %>% 
  filter(label == "e") %>% 
  select(est)
heritability_rrb_18 <- print(estA[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))
```

##RRB @ 36 months  
```{r, warning = FALSE, message = F}
#ACE model
ACE_36 <-'

# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*rrb36_0 + c(a,a)*rrb36_0
  A2=~ NA*rrb36_1 + c(a,a)*rrb36_1 
  C =~ NA*rrb36_0 + NA*rrb36_1 + c(c,c)*rrb36_0 + c(c,c)*rrb36_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  C ~~ 1*C
  rrb36_0~~c(e,e)*rrb36_0
  rrb36_1~~c(e,e)*rrb36_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  C ~~ 0*A1 + 0*A2
'
ACE_36.fit <- cfa(ACE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
semPaths(ACE_36.fit)
semPaths(ACE_36.fit, what = "std")

#ADE model

#CE model

#AE model

#Model comparisons

##Summarizing fit for preferred model
summary(ACE_36.fit)
fitMeasures(ACE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))

#Calculating heritability for preferred model
estA <- as_tibble(parameterEstimates(ACE_36.fit)) %>% 
  filter(label == "a") %>% 
  select(est)
estC <- as_tibble(parameterEstimates(ACE_36.fit)) %>% 
  filter(label == "c") %>% 
  select(est)
estE <- as_tibble(parameterEstimates(ACE_36.fit)) %>% 
  filter(label == "e") %>% 
  select(est)
heritability_rrb36_36 <- print(estA[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))
```





