---
title: "ASD_ACE"
author: "Zoë Hawks"
date: "11/9/2017"
output: pdf_document
---

##Setting up dataframe
```{r, warning = FALSE, message = FALSE}
library(lavaan)
library(semPlot)
library(tidyverse)
library(dplyr)
library(forcats)

setwd("/Users/zashawks/Desktop/Stats/Longitudinal/ALDA")
mydata <- read.csv("ASD_master_data_stats.csv", header=TRUE)  

mydata_wide <- mydata %>% 
  select(famid, Random_twin_assignment, zy_final_all, sci, rrb, rrb_30_36, sci_30_36) %>%
  rename("sci36" = "sci_30_36", "rrb36" = "rrb_30_36") %>%
  filter(!is.na(Random_twin_assignment), zy_final_all == 1 | zy_final_all == 2 | zy_final_all == 5) %>%
  mutate(zy_final_all = ifelse((zy_final_all == 5 | zy_final_all == 2), 2, 1)) %>%
  mutate_at(c("zy_final_all"), funs(as.factor(.))) %>%
  mutate(zy_final_all = factor(zy_final_all, labels = c("MZ", "DZ"))) %>%
  mutate_at(c("sci", "rrb", "rrb36", "sci36"), funs(as.numeric(.))) %>%
  gather(-(famid:zy_final_all), key = "variable", value = "value") %>%
  unite(varT, variable, Random_twin_assignment) %>%
  spread(key = varT, value = value)

##Corstars function
corstars <-function(x, method=c("pearson", "spearman"), removeTriangle=c("upper", "lower"),
                     result=c("none", "html", "latex")){
    #Compute correlation matrix
    require(Hmisc)
    x <- as.matrix(x)
    correlation_matrix<-rcorr(x, type=method[1])
    R <- correlation_matrix$r # Matrix of correlation coeficients
    p <- correlation_matrix$P # Matrix of p-value 
    
    ## Define notions for significance levels; spacing is important.
    mystars <- ifelse(p < .001, "***", ifelse(p < .001, "*** ", 
                                              ifelse(p < .01, "**  ", 
                                                     ifelse(p < .05, "*   ", "    "))))
    
    ## trunctuate the correlation matrix to two decimal
    R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
    
    ## build a new matrix that includes the correlations with their apropriate stars
    Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
    diag(Rnew) <- paste(diag(R), " ", sep="")
    rownames(Rnew) <- colnames(x)
    colnames(Rnew) <- paste(colnames(x), "", sep="")
    
    ## remove upper triangle of correlation matrix
    if(removeTriangle[1]=="upper"){
      Rnew <- as.matrix(Rnew)
      Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove lower triangle of correlation matrix
    else if(removeTriangle[1]=="lower"){
      Rnew <- as.matrix(Rnew)
      Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }

} 
```

##Hypotheses  

Given previous evidence in children indicating that autistic traits are highly heritable, we predict heritability on the order of roughly 70-90% for our social communicative (SCI) and repetitive behaviors (RRB) factors. However, it is unclear (1) whether genetic effects will be this large in infancy and (2) how this effect may change over the course of early development (i.e., 18 to 36 months).  
  
Some background on biometric models:  

* A = additive effects stemming from shared genetic material (MZ share 100%, DZ share 50%)  
* D = non-additive effects (e.g., dominance effects; MZ = share both alleles at 100% of loci, DZ = share both alleles at 25% of loci)  
* C = shared environmental effects (e.g., prenatal, shared home)  
* E = non-shared environment (e.g., different peer groups, attending different schools)  
* Common to test different models based on hypotheses about genetic and environmental structure of construct -- ACE, ADE, CE, AE  

##Visualizing data
```{r, warning = FALSE, message = F}
#Assessing attrition
mydata_wide %>% 
  summarise_at(vars(c("rrb_0", "rrb36_0", "sci_0", "sci36_0")), funs(sum(!is.na(.))))

#Correlation tables
RRB_corr <- print(corstars(mydata_wide %>% select(rrb_0, rrb_1, rrb36_0, rrb36_1)))
SCI_corr <- print(corstars(mydata_wide %>% select(sci_0, sci_1, sci36_0, sci36_1)))

#To what extent is skewed data an issue?
hist(mydata$rrb)
hist(mydata$rrb_30_36)
hist(mydata$sci)
hist(mydata$sci_30_36)

#GGplot to graph change over time
mydata_long_rrb <- mydata %>% 
  select(identno, rrb, rrb_30_36, sci, sci_30_36) %>%
  gather(-identno, key = "Age", value = "value") %>%
  mutate_at(c("Age"), funs(as.factor(.))) %>%
  separate(Age, into = c("Trait", "Age"), sep = c(2)) %>%
  mutate(Age = ifelse((Age == "b" | Age == "i"), "18", "36")) %>%
  mutate(Trait = ifelse((Trait == "rr"), "RRB", "SCI"))

mydata_long_rrb <- data.frame(mydata_long_rrb)
ggplot(data=mydata_long_rrb, aes(x=Age, y=value, fill = Trait)) +
    geom_bar(stat="identity", position=position_dodge()) +
  xlab("Age (in months)") +
  ylab("Trait Score") +
  scale_fill_manual(values=c("cornflowerblue", "darkgoldenrod2"))
```

##RRB @ 18 months  
```{r, warning = FALSE, message = F}
##################### ACE model ########################

ACE_18 <-'

# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*rrb_0 + c(a,a)*rrb_0
  A2=~ NA*rrb_1 + c(a,a)*rrb_1 
  C =~ NA*rrb_0 + NA*rrb_1 + c(c,c)*rrb_0 + c(c,c)*rrb_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  C ~~ 1*C
  rrb_0~~c(e,e)*rrb_0
  rrb_1~~c(e,e)*rrb_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  C ~~ 0*A1 + 0*A2
'
ACE_18.fit <- cfa(ACE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(ACE_18.fit)
fitMeasures(ACE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(ACE_18.fit)
semPaths(ACE_18.fit, what = "std")

##################### ADE model ########################

ADE_18 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*rrb_0 + c(a,a)*rrb_0 
  A2=~ NA*rrb_1 + c(a,a)*rrb_1 
  D1 =~ NA*rrb_0 + c(d,d)*rrb_0
  D2 =~ NA*rrb_1 + c(d,d)*rrb_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  D1 ~~ 1*D1
  D2 ~~ 1*D2
  rrb_0~~c(e,e)*rrb_0
  rrb_1~~c(e,e)*rrb_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  A1 ~~ 0*D1 + 0*D2
  A2 ~~ 0*D1 + 0*D2
  D1 ~~ c(1,.25)*D2
'
ADE_18.fit <- cfa(ADE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(ADE_18.fit)
fitMeasures(ADE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(ADE_18.fit)
semPaths(ADE_18.fit, what = "std")

##################### CE model ########################

CE_18 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  C =~ NA*rrb_0 + NA*rrb_1 + c(c,c)*rrb_0 + c(c,c)*rrb_1

# constrain the factor variances (fixed factor method)

  C ~~ 1*C
  rrb_0~~c(e,e)*rrb_0
  rrb_1~~c(e,e)*rrb_1
'
CE_18.fit <- cfa(CE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(CE_18.fit)
fitMeasures(CE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(CE_18.fit)
semPaths(CE_18.fit, what = "std")

##################### AE model ########################

AE_18 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*rrb_0 + c(a,a)*rrb_0 
  A2=~ NA*rrb_1 + c(a,a)*rrb_1 

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  rrb_0~~c(e,e)*rrb_0
  rrb_1~~c(e,e)*rrb_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
'
AE_18.fit <- cfa(AE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
fitMeasures(AE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
summary(AE_18.fit)
semPaths(AE_18.fit)
semPaths(AE_18.fit, what = "std")

#Model comparisons; left out CE model because we're interested in heritability
#AE model is preferred because larger Df (indicating fewer constraints, simpler model) and lower AIC, BIC
#Interested in ACE parameters, so that's what I'll focus on below
anova(AE_18.fit, ACE_18.fit, ADE_18.fit)

##Summarizing fit ACE model
summary(ACE_18.fit)
fitMeasures(ACE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))

#Calculating heritability for preferred model
estA <- as_tibble(parameterEstimates(ACE_18.fit)) %>%
  filter(label == "a") %>%
  select(est)
estC <- as_tibble(parameterEstimates(ACE_18.fit)) %>%
  filter(label == "c") %>%
  select(est)
estE <- as_tibble(parameterEstimates(ACE_18.fit)) %>%
  filter(label == "e") %>%
  select(est)
heritability_rrb_18 <- print(estA[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))
commonenviron_rrb_18 <- print(estC[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))
environ_rrb_18 <- print(estE[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))

RRB_ACE_18.fit <- ACE_18.fit
```

* Fit measures: TLI = 1.006, CFI = 1.000, RMSEA = 0.000, SRMR = .080
* Heritability = 66.3%
* Common environment = 0% (we can see why the AE model was preferred...)
* Uncommon environment = 33.7%

##RRB @ 36 months  
```{r, warning = FALSE, message = F}
##################### ACE model ########################

ACE_36 <-'

# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*rrb36_0 + c(a,a)*rrb36_0
  A2=~ NA*rrb36_1 + c(a,a)*rrb36_1 
  C =~ NA*rrb36_0 + NA*rrb36_1 + c(c,c)*rrb36_0 + c(c,c)*rrb36_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  C ~~ 1*C
  rrb36_0~~c(e,e)*rrb36_0
  rrb36_1~~c(e,e)*rrb36_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  C ~~ 0*A1 + 0*A2
'
ACE_36.fit <- cfa(ACE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(ACE_36.fit)
fitMeasures(ACE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(ACE_36.fit)
semPaths(ACE_36.fit, what = "std")

##################### ADE model ########################

ADE_36 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*rrb_0 + c(a,a)*rrb_0 
  A2=~ NA*rrb_1 + c(a,a)*rrb_1 
  D1 =~ NA*rrb_0 + c(d,d)*rrb_0
  D2 =~ NA*rrb_1 + c(d,d)*rrb_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  D1 ~~ 1*D1
  D2 ~~ 1*D2
  rrb_0~~c(e,e)*rrb_0
  rrb_1~~c(e,e)*rrb_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  A1 ~~ 0*D1 + 0*D2
  A2 ~~ 0*D1 + 0*D2
  D1 ~~ c(1,.25)*D2
'
ADE_36.fit <- cfa(ADE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
fitMeasures(ADE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
summary(ADE_36.fit)
semPaths(ADE_36.fit)
semPaths(ADE_36.fit, what = "std")

##################### CE model ########################

CE_36 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  C =~ NA*rrb36_0 + NA*rrb36_1 + c(c,c)*rrb36_0 + c(c,c)*rrb36_1

# constrain the factor variances (fixed factor method)

  C ~~ 1*C
  rrb36_0~~c(e,e)*rrb36_0
  rrb36_1~~c(e,e)*rrb36_1
'
CE_36.fit <- cfa(CE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(CE_36.fit)
fitMeasures(CE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(CE_36.fit)
semPaths(CE_36.fit, what = "std")

##################### AE model ########################

AE_36 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*rrb36_0 + c(a,a)*rrb36_0 
  A2=~ NA*rrb36_1 + c(a,a)*rrb36_1 

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  rrb36_0~~c(e,e)*rrb36_0
  rrb36_1~~c(e,e)*rrb36_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
'
AE_36.fit <- cfa(AE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(AE_36.fit)
fitMeasures(AE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(AE_36.fit)
semPaths(AE_36.fit, what = "std")

#Model comparisons; left out CE model because interested in heritability
#Again, AE model is preferred (despite the fact that fit statistics looked much better for ADE model)
#Interested in ACE parameters, so that's what I'll focus on below
anova(ACE_36.fit, ADE_36.fit, AE_36.fit)

#Summarizing fit for ACE model
#Fit statistics are terrible, possibly due to small sample size. 
#Not sure how much of an issue this is for biometric models...?
summary(ACE_36.fit)
fitMeasures(ACE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))

#Calculating heritability for preferred model
estA <- as_tibble(parameterEstimates(ACE_36.fit)) %>%
  filter(label == "a") %>%
  select(est)
estC <- as_tibble(parameterEstimates(ACE_36.fit)) %>%
  filter(label == "c") %>%
  select(est)
estE <- as_tibble(parameterEstimates(ACE_36.fit)) %>%
  filter(label == "e") %>%
  select(est)
heritability_rrb36_36 <- print(estA[1,1]/(estA[1,1] + estE[1,1]))
commonenviron_rrb_36 <- print(estC[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))
environ_rrb_36 <- print(estE[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))

RRB_ACE_36.fit <- ACE_36.fit
```

* Fit measures: TLI = -0.122, CFI = 0.000, RMSEA = 0.485, SRMR = 1.032
* Heritability = 84.7% (compare to 66.3% at 18 months)
* Common environment = 0% (we can see why the AE model was preferred...)
* Uncommon environment = 15.3% (compare to 33.7% at 18 months)
* Heritability appears to increase during early development. Measurement artifcat? Genetic effects come online?

##SCI @ 18 months
```{r, message = FALSE, warning = FALSE}
##################### ACE model ########################

ACE_18 <-'

# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*sci_0 + c(a,a)*sci_0
  A2=~ NA*sci_1 + c(a,a)*sci_1 
  C =~ NA*sci_0 + NA*sci_1 + c(c,c)*sci_0 + c(c,c)*sci_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  C ~~ 1*C
  sci_0~~c(e,e)*sci_0
  sci_1~~c(e,e)*sci_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  C ~~ 0*A1 + 0*A2
'
ACE_18.fit <- cfa(ACE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(ACE_18.fit)
fitMeasures(ACE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(ACE_18.fit)
semPaths(ACE_18.fit, what = "std")

##################### ADE model ########################

ADE_18 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*sci_0 + c(a,a)*sci_0 
  A2=~ NA*sci_1 + c(a,a)*sci_1 
  D1 =~ NA*sci_0 + c(d,d)*sci_0
  D2 =~ NA*sci_1 + c(d,d)*sci_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  D1 ~~ 1*D1
  D2 ~~ 1*D2
  sci_0~~c(e,e)*sci_0
  sci_1~~c(e,e)*sci_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  A1 ~~ 0*D1 + 0*D2
  A2 ~~ 0*D1 + 0*D2
  D1 ~~ c(1,.25)*D2
'
ADE_18.fit <- cfa(ADE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(ADE_18.fit)
fitMeasures(ADE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(ADE_18.fit)
semPaths(ADE_18.fit, what = "std")

##################### CE model ########################

CE_18 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  C =~ NA*sci_0 + NA*sci_1 + c(c,c)*sci_0 + c(c,c)*sci_1

# constrain the factor variances (fixed factor method)

  C ~~ 1*C
  sci_0~~c(e,e)*sci_0
  sci_1~~c(e,e)*sci_1
'
CE_18.fit <- cfa(CE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(CE_18.fit)
fitMeasures(CE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(CE_18.fit)
semPaths(CE_18.fit, what = "std")

##################### AE model ########################

AE_18 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*sci_0 + c(a,a)*sci_0 
  A2=~ NA*sci_1 + c(a,a)*sci_1 

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  sci_0~~c(e,e)*sci_0
  sci_1~~c(e,e)*sci_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
'
AE_18.fit <- cfa(AE_18, data = mydata_wide, missing = "ML", group = "zy_final_all")
fitMeasures(AE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
summary(AE_18.fit)
semPaths(AE_18.fit)
semPaths(AE_18.fit, what = "std")

#Model comparisons; left out CE model because we're interested in heritability
#AE model is preferred because larger Df (indicating fewer constraints, simpler model) and lower AIC, BIC
#Interested in ACE parameters, so that's what I'll focus on below
anova(AE_18.fit, ACE_18.fit, ADE_18.fit)

##Summarizing fit ACE model
#Model fit isn't terrrrible, but not great either
summary(ACE_18.fit)
fitMeasures(ACE_18.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))

#Calculating heritability for preferred model
estA <- as_tibble(parameterEstimates(ACE_18.fit)) %>%
  filter(label == "a") %>%
  select(est)
estC <- as_tibble(parameterEstimates(ACE_18.fit)) %>%
  filter(label == "c") %>%
  select(est)
estE <- as_tibble(parameterEstimates(ACE_18.fit)) %>%
  filter(label == "e") %>%
  select(est)
heritability_sci_18 <- print(estA[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))
commonenviron_sci_18 <- print(estC[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))
environ_sci_18 <- print(estE[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))

SCI_ACE_18.fit <- ACE_18.fit
```

* Fit measures: TLI = 0.899, CFI = .848, RMSEA = 0.266, SRMR = .212
* Heritability = 47.4%
* Common environment = 0% (again, we can see why the AE model was preferred)
* Uncommon environment = 52.6%%

##SCI @ 36 months
```{r, warning = FALSE, message = F}
##################### ACE model ########################

ACE_36 <-'

# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*sci36_0 + c(a,a)*sci36_0
  A2=~ NA*sci36_1 + c(a,a)*sci36_1 
  C =~ NA*sci36_0 + NA*sci36_1 + c(c,c)*sci36_0 + c(c,c)*sci36_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  C ~~ 1*C
  sci36_0~~c(e,e)*sci36_0
  sci36_1~~c(e,e)*sci36_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  C ~~ 0*A1 + 0*A2
'
ACE_36.fit <- cfa(ACE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(ACE_36.fit)
fitMeasures(ACE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(ACE_36.fit)
semPaths(ACE_36.fit, what = "std")

##################### ADE model ########################

ADE_36 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*sci_0 + c(a,a)*sci_0 
  A2=~ NA*sci_1 + c(a,a)*sci_1 
  D1 =~ NA*sci_0 + c(d,d)*sci_0
  D2 =~ NA*sci_1 + c(d,d)*sci_1

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  D1 ~~ 1*D1
  D2 ~~ 1*D2
  sci_0~~c(e,e)*sci_0
  sci_1~~c(e,e)*sci_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
  A1 ~~ 0*D1 + 0*D2
  A2 ~~ 0*D1 + 0*D2
  D1 ~~ c(1,.25)*D2
'
ADE_36.fit <- cfa(ADE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
fitMeasures(ADE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
summary(ADE_36.fit)
semPaths(ADE_36.fit)
semPaths(ADE_36.fit, what = "std")

##################### CE model ########################

CE_36 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  C =~ NA*sci36_0 + NA*sci36_1 + c(c,c)*sci36_0 + c(c,c)*sci36_1

# constrain the factor variances (fixed factor method)

  C ~~ 1*C
  sci36_0~~c(e,e)*sci36_0
  sci36_1~~c(e,e)*sci36_1
'
CE_36.fit <- cfa(CE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(CE_36.fit)
fitMeasures(CE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(CE_36.fit)
semPaths(CE_36.fit, what = "std")

##################### AE model ########################

AE_36 <-'
# build the factor model with group constraints
# E is residual -- non-shared environment so do not need to model
# Want indicators (1) free to vary but (2) constrained to be equivalent

  A1=~ NA*sci36_0 + c(a,a)*sci36_0 
  A2=~ NA*sci36_1 + c(a,a)*sci36_1 

# constrain the factor variances (fixed factor method)

  A1 ~~ 1*A1
  A2 ~~ 1*A2
  sci36_0~~c(e,e)*sci36_0
  sci36_1~~c(e,e)*sci36_1

# constrain the factor covariances 
# this is where we account for differences in shared genetic background between MZ & DZ twins

  A1 ~~ c(1,.5)*A2
'
AE_36.fit <- cfa(AE_36, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(AE_36.fit)
fitMeasures(AE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
semPaths(AE_36.fit)
semPaths(AE_36.fit, what = "std")

#Model comparisons; left out CE model because interested in heritability
#Again, AE model is preferred 
#Interested in ACE parameters, so that's what I'll focus on below
anova(ACE_36.fit, ADE_36.fit, AE_36.fit)

#Summarizing fit for ACE model
#Fit statistics are pretty bad, consistent with 36-mo. RRB model. Due to reduced sample size at 36 months?
summary(ACE_36.fit)
fitMeasures(ACE_36.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))

#Calculating heritability for preferred model
estA <- as_tibble(parameterEstimates(ACE_36.fit)) %>%
  filter(label == "a") %>%
  select(est)
estC <- as_tibble(parameterEstimates(ACE_36.fit)) %>%
  filter(label == "c") %>%
  select(est)
estE <- as_tibble(parameterEstimates(ACE_36.fit)) %>%
  filter(label == "e") %>%
  select(est)
heritability_sci36_36 <- print(estA[1,1]/(estA[1,1] + estE[1,1]))
commonenviron_sci_36 <- print(estC[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))
environ_sci_36 <- print(estE[1,1]/(estA[1,1] + estC[1,1] + estE[1,1]))

SCI_ACE_36.fit <- ACE_36.fit
```

* Fit measures: TLI = .579, CFI = 0.368, RMSEA = 0.387, SRMR = .579
* Heritability = 73.9% (compare to 47.4% at 18 months)
* Common environment = 0% (we can see why the AE model was preferred...)
* Uncommon environment = 26.1% (compare to 52.6% at 18 months)
* As with RRB, heritability appears to increase during early development.
* Heritability of SCI appears reduced relative to heritability of RRB.

##Longitudinal biometric model for RRB  

*Ran Cholesky model rather than latent growth curve model because scale used to assess SCI and RRB at 18 months (vrRSB) differs from scale used to assess these constructs at 36 months (SRS-2)*
```{r}

ACE_long <- '

# Constructing model at 18 months & specifying paths between models

  A1_1 =~ NA*rrb_0 + c(a1,a1)*rrb_0 + NA*rrb36_0
  A2_1 =~ NA*rrb_1 + c(a1,a1)*rrb_1 + NA*rrb36_1
  C_1 =~ NA*rrb_0 + NA*rrb_1 + c(c1,c1)*rrb_0 + c(c1,c1)*rrb_1 + NA*rrb36_0 + NA*rrb36_1

  A1_1 ~~ 1*A1_1
  A2_1 ~~ 1*A2_1
  C_1 ~~ 1*C_1
  rrb_0~~c(e1,e1)*rrb_0
  rrb_1~~c(e1,e1)*rrb_1

  A1_1 ~~ c(1,.5)*A2_1
  C_1 ~~ 0*A1_1 + 0*A2_1

# Constructing model at 36 months and specifying longitudinal relationships between latent constructs
# Constrain long. associations so that value is the same for twin 1 and twin 2

  A1_2 =~ NA*rrb36_0 + c(a2,a2)*rrb36_0 
  A2_2 =~ NA*rrb36_1 + c(a2,a2)*rrb36_1 
  C_2 =~ NA*rrb36_0 + NA*rrb36_1 + c(c2,c2)*rrb36_0 + c(c2,c2)*rrb36_1

  A1_2 ~~ 1*A1_2 
  A2_2 ~~ 1*A2_2 
  C_2 ~~ 1*C_2 
  rrb36_0 ~~c(e2,e2)*rrb36_0
  rrb36_1 ~~c(e2,e2)*rrb36_1

  A1_2 ~~ c(1,.5)*A2_2 
  C_2 ~~ 0*A1_2 + 0*A2_2 

# Specifying longitudinal relationships between latent constructs

  A1_2 ~~ NA*A1_1 + 0*A2_1 + 0*C_1
  A2_2 ~~ NA*A2_1 + 0*A1_1 + 0*C_1
  C_2 ~~ NA*C_1 + 0*A1_1 + 0*A2_1
'

ACE_long.fit <- cfa(ACE_long, data = mydata_wide, missing = "ML", group = "zy_final_all")
summary(ACE_long.fit)
semPaths(ACE_long.fit)

#Model didn't converge -- "covariance is not positive definite"
inspect(ACE_long.fit, "cov.lv")
```

