---
title: "SEM & Lavaan part 2"
author: "Zoë Hawks"
date: "10/27/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, include = FALSE, message = FALSE, warning = FALSE}
#importing datasets
setwd("/Users/zashawks/Desktop/PNL/PKU/Verbal Fluency/Round 2 Analyses")
mydata <- read.csv("Master_data-new.csv", header = T)

setwd("/Users/zashawks/Desktop/Stats/Longitudinal/ALDA")
library(tidyverse)
library(tibble)
library(lubridate)
library(lavaan)
library(semPlot)
library(semTools)
library(dplyr)
library(tidyverse)
library(MASS)
library(psych)

#Converting group into factor variable (0 = Control, 1 = PKU)
mydata$GROUP <- as.factor(mydata$GROUP)

#Creating averages
mydata$Sem_TotalCorrect <- (mydata$Animal_TotalCorrect + mydata$Food_TotalCorrect)
mydata$Pho_TotalCorrect <- (mydata$F_TotalCorrect + mydata$S_TotalCorrect)

mydata$Sem_TotalUtterances <- (mydata$Animal_TotalUtterances + mydata$Food_TotalUtterances)
mydata$Pho_TotalUtterances <- (mydata$F_TotalUtterances + mydata$S_TotalUtterances)

mydata$Sem_Switches <- (mydata$Animal_Switches + mydata$Food_Switches)
mydata$Pho_Switches <- (mydata$F_Switches + mydata$S_Switches)

mydata$Sem_N_Clusters <- (mydata$Animal_N_Clusters + mydata$Food_N_Clusters)
mydata$Pho_N_Clusters <- (mydata$F_N_Clusters + mydata$S_N_Clusters)

mydata$Sem_TW_Clusters <- (mydata$Animal_TW_Clusters + mydata$Food_TW_Clusters)
mydata$Pho_TW_Clusters <- (mydata$F_TW_Clusters + mydata$S_TW_Clusters)

mydata$Animal_Mean_Clusters <- mydata$Animal_TW_Clusters/mydata$Animal_N_Clusters
mydata$Food_Mean_Clusters <- mydata$Food_TW_Clusters/mydata$Food_N_Clusters
mydata$F_Mean_Clusters <- mydata$F_TW_Clusters/mydata$F_N_Clusters
mydata$S_Mean_Clusters <- mydata$S_TW_Clusters/mydata$S_N_Clusters

mydata$Sem_Mean_Clusters <- (mydata$Animal_Mean_Clusters + mydata$Food_Mean_Clusters)
mydata$Pho_Mean_Clusters <- (mydata$F_Mean_Clusters + mydata$S_Mean_Clusters)

mydata$Sem_Errors <- (mydata$Animal_TotalUtterances + mydata$Food_TotalUtterances) -
  (mydata$Animal_TotalCorrect + mydata$Food_TotalCorrect)
mydata$Pho_Errors <- (mydata$F_TotalUtterances + mydata$S_TotalUtterances) -
  (mydata$F_TotalCorrect + mydata$S_TotalCorrect)

mydata$Sem_Singletons <- (mydata$Animal_TotalUtterances + mydata$Food_TotalUtterances) -
  (mydata$Animal_TW_Clusters + mydata$Food_TW_Clusters) - 
  (mydata$Animal_N_Clusters + mydata$Food_N_Clusters)
mydata$Pho_Singletons <- (mydata$F_TotalUtterances + mydata$S_TotalUtterances) -
  (mydata$F_TW_Clusters + mydata$S_TW_Clusters) -
  (mydata$F_N_Clusters + mydata$S_N_Clusters)
```

```{r, warning=FALSE, message=FALSE, include = FALSE}
##Raw score distributions & normalization
#Total Correct
hist(mydata$Sem_TotalCorrect)
qqnorm(mydata$Sem_TotalCorrect)
qqline(mydata$Sem_TotalCorrect)

hist(mydata$Pho_TotalCorrect)
qqnorm(mydata$Pho_TotalCorrect)
qqline(mydata$Pho_TotalCorrect)

psych::describe(mydata$Sem_TotalCorrect)
psych::describe(mydata$Pho_TotalCorrect)

#Phomenic data aren't normally distributed --> apply transformation
#Determining optimal lambda
trans1 <- boxcox(lm(mydata$Pho_TotalCorrect ~ 1), plotit = T)
range(trans1$x[trans1$y > max(trans1$y)-qchisq(0.95,1)/2]) #95% lambda range
trans_df = as.data.frame(trans1) #optimal lambda
optimal_lambda1 = trans_df[which.max(trans1$y),1]
optimal_lambda1 #optimal lambda = .2626263
#Applying transform to data
mydata$Pho_TotalCorrect_BOX <- (mydata$Pho_TotalCorrect)^optimal_lambda1
describe(mydata$Pho_TotalCorrect_BOX)
hist(mydata$Pho_TotalCorrect_BOX)
qqnorm(mydata$Pho_TotalCorrect_BOX)
qqline(mydata$Pho_TotalCorrect_BOX)
mydata$Pho_TotalCorrect_BOX <- scale(mydata$Pho_TotalCorrect_BOX) #z-score Box-Cox transforms

##############################

#Switches
hist(mydata$Sem_Switches)
qqnorm(mydata$Sem_Switches)
qqline(mydata$Sem_Switches)

hist(mydata$Pho_Switches)
qqnorm(mydata$Pho_Switches)
qqline(mydata$Pho_Switches)

psych::describe(mydata$Sem_Switches)

#Phomenic data aren't normally distributed --> apply transformation
#Determining optimal lambda
trans1 <- boxcox(lm(mydata$Pho_Switches ~ 1), plotit = T)
range(trans1$x[trans1$y > max(trans1$y)-qchisq(0.95,1)/2]) #95% lambda range
trans_df = as.data.frame(trans1) #optimal lambda
optimal_lambda1 = trans_df[which.max(trans1$y),1]
optimal_lambda1 #optimal labmda = .1010101
#Applying transform to data
mydata$Pho_Switches_BOX <- (mydata$Pho_Switches)^optimal_lambda1
describe(mydata$Pho_Switches_BOX)
hist(mydata$Pho_Switches_BOX)
qqnorm(mydata$Pho_Switches_BOX)
qqline(mydata$Pho_Switches_BOX)
mydata$Pho_Switches_BOX <- scale(mydata$Pho_Switches_BOX)

##########################

#N_Clusters
hist(mydata$Sem_N_Clusters)
qqnorm(mydata$Sem_N_Clusters)
qqline(mydata$Sem_N_Clusters)

hist(mydata$Pho_N_Clusters)
qqnorm(mydata$Pho_N_Clusters)
qqline(mydata$Pho_N_Clusters)

psych::describe(mydata$Sem_N_Clusters)
psych::describe(mydata$Pho_N_Clusters)

#Phomenic data aren't normally distributed --> apply transformation
#Determining optimal lambda
trans1 <- boxcox(lm(mydata$Pho_N_Clusters ~ 1), plotit = T)
range(trans1$x[trans1$y > max(trans1$y)-qchisq(0.95,1)/2]) #95% lambda range
trans_df = as.data.frame(trans1) #optimal lambda
optimal_lambda1 = trans_df[which.max(trans1$y),1]
optimal_lambda1 #optimal lambda = .3434343
#Applying transform to data
mydata$Pho_N_Clusters_BOX <- (mydata$Pho_N_Clusters)^optimal_lambda1
psych::describe(mydata$Pho_N_Clusters_BOX)
hist(mydata$Pho_N_Clusters_BOX)
qqnorm(mydata$Pho_N_Clusters_BOX)
qqline(mydata$Pho_N_Clusters_BOX)
mydata$Pho_N_Clusters_BOX <- scale(mydata$Pho_N_Clusters_BOX)

#########################

#TotalUtterances
hist(mydata$Sem_TotalUtterances)
qqnorm(mydata$Sem_TotalUtterances)
qqline(mydata$Sem_TotalUtterances)

hist(mydata$Pho_TotalUtterances)
qqnorm(mydata$Pho_TotalUtterances)
qqline(mydata$Pho_TotalUtterances)

psych::describe(mydata$Sem_TotalUtterances)
psych::describe(mydata$Pho_TotalUtterances)

#Phomenic data aren't normally distributed --> apply transformation
#Determining optimal lambda
trans1 <- boxcox(lm(mydata$Pho_TotalUtterances ~ 1), plotit = T)
range(trans1$x[trans1$y > max(trans1$y)-qchisq(0.95,1)/2]) #95% lambda range
trans_df = as.data.frame(trans1) #optimal lambda
optimal_lambda1 = trans_df[which.max(trans1$y),1]
optimal_lambda1 #.06060606
#Applying transform to data
mydata$Pho_TotalUtterances_BOX <- (mydata$Pho_TotalUtterances)^optimal_lambda1
describe(mydata$Pho_TotalUtterances_BOX)
hist(mydata$Pho_TotalUtterances_BOX)
qqnorm(mydata$Pho_TotalUtterances_BOX)
qqline(mydata$Pho_TotalUtterances_BOX)
mydata$Pho_TotalUtterances_BOX <- scale(mydata$Pho_TotalUtterances_BOX)

#########################

#TW_Clusters
hist(mydata$Sem_TW_Clusters)
qqnorm(mydata$Sem_TW_Clusters)
qqline(mydata$Sem_TW_Clusters)

hist(mydata$Pho_TW_Clusters)
qqnorm(mydata$Pho_TW_Clusters)
qqline(mydata$Pho_TW_Clusters)

# psych::describe(mydata$Sem_TW_Clusters)
# mydata <- subset(mydata,!(mydata$Sem_TW_Clusters < 0))
# psych::describe(mydata$Sem_TW_Clusters)
# psych::describe(mydata$Pho_TW_Clusters)

#Phomenic data aren't normally distributed --> apply transformation
#Determining optimal lambda
trans1 <- boxcox(lm(mydata$Pho_TW_Clusters ~ 1), plotit = T)
range(trans1$x[trans1$y > max(trans1$y)-qchisq(0.95,1)/2]) #95% lambda range
trans_df = as.data.frame(trans1) #optimal lambda
optimal_lambda1 = trans_df[which.max(trans1$y),1]
optimal_lambda1 #optimal lambda = .3030303
#Applying transform to data
mydata$Pho_TW_Clusters_BOX <- (mydata$Pho_TW_Clusters)^optimal_lambda1
describe(mydata$Pho_TW_Clusters_BOX)
hist(mydata$Pho_TW_Clusters_BOX)
qqnorm(mydata$Pho_TW_Clusters_BOX)
qqline(mydata$Pho_TW_Clusters_BOX)
mydata$Pho_TW_Clusters_BOX <- scale(mydata$Pho_TW_Clusters_BOX)

###############################

#ERRORS
#Determining optimal lambda
psych::describe(mydata$Pho_Errors)
mydata$Pho_Errors_Plus <- mydata$Pho_Errors + 1
trans1 <- boxcox(lm(mydata$Pho_Errors_Plus ~ 1), plotit = T)
range(trans1$x[trans1$y > max(trans1$y)-qchisq(0.95,1)/2]) #95% lambda range
trans_df = as.data.frame(trans1) #optimal lambda
optimal_lambda1 = trans_df[which.max(trans1$y),1]
optimal_lambda1 #optimal labmda = .3434343
#Applying transform to data
mydata$Pho_Errors_BOX <- (mydata$Pho_Errors)^optimal_lambda1
psych::describe(mydata$Pho_Errors_BOX)
hist(mydata$Pho_Errors_BOX)
qqnorm(mydata$Pho_Errors_BOX)
qqline(mydata$Pho_Errors_BOX)
mydata$Pho_Errors_BOX <- scale(mydata$Pho_Errors_BOX)

##############################

#Singletons
#Determining optimal lambda
psych::describe(mydata$Pho_Singletons)
trans1 <- boxcox(lm(mydata$Pho_Singletons ~ 1), plotit = T)
range(trans1$x[trans1$y > max(trans1$y)-qchisq(0.95,1)/2]) #95% lambda range
trans_df = as.data.frame(trans1) #optimal lambda
optimal_lambda1 = trans_df[which.max(trans1$y),1]
optimal_lambda1 #optimal labmda = .1414141
#Applying transform to data
mydata$Pho_Singletons_BOX <- (mydata$Pho_Singletons)^optimal_lambda1
psych::describe(mydata$Pho_Singletons_BOX)
hist(mydata$Pho_Singletons_BOX)
qqnorm(mydata$Pho_Singletons_BOX)
qqline(mydata$Pho_Singletons_BOX)
mydata$Pho_Singletons_BOX <- scale(mydata$Pho_Singletons_BOX)

##############################

#Mean_Clusters
#Determining optimal lambda
psych::describe(mydata$Pho_Mean_Clusters)
trans1 <- boxcox(lm(mydata$Pho_Mean_Clusters ~ 1), plotit = T)
range(trans1$x[trans1$y > max(trans1$y)-qchisq(0.95,1)/2]) #95% lambda range
trans_df = as.data.frame(trans1) #optimal lambda
optimal_lambda1 = trans_df[which.max(trans1$y),1]
optimal_lambda1 #optimal labmda = -.9090909
#Applying transform to data
mydata$Pho_Mean_Clusters_BOX <- (mydata$Pho_Mean_Clusters)^optimal_lambda1
psych::describe(mydata$Pho_Mean_Clusters_BOX)
hist(mydata$Pho_Mean_Clusters_BOX)
qqnorm(mydata$Pho_Mean_Clusters_BOX)
qqline(mydata$Pho_Mean_Clusters_BOX)
mydata$Pho_Mean_Clusters_BOX <- scale(mydata$Pho_Mean_Clusters_BOX)

###################################

##Long to wide form
mydata_wide <- mydata %>% dplyr::select(-Age_at_timepoint_1) %>%
  gather(-c(ID2, Timepoint, GROUP), key = "variable", value = "value") %>%
  unite(varT, variable, Timepoint) %>%
  spread(key = varT, value = value)

mydata_wide$Animal_TW_Clusters_1 <- as.numeric(scale(as.numeric(mydata_wide$Animal_TW_Clusters_1)))
mydata_wide$Food_TW_Clusters_1 <- as.numeric(scale(as.numeric(mydata_wide$Food_TW_Clusters_1)))
mydata_wide$Food_Switches_1 <- as.numeric(scale(as.numeric(mydata_wide$Food_Switches_1)))
mydata_wide$Animal_Switches_1 <- as.numeric(scale(as.numeric(mydata_wide$Animal_Switches_1)))
mydata_wide$IQ_vocraw_1 <- as.numeric(scale(as.numeric(mydata_wide$IQ_vocraw_1)))
mydata_wide$IQ_mrraw_1 <- as.numeric(scale(as.numeric(mydata_wide$IQ_mrraw_1)))
mydata_wide$GROUP <- as.factor(mydata_wide$GROUP) 
mydata_wide$Age_at_time_of_testing_1 <- as.numeric(mydata_wide$Age_at_time_of_testing_1) 
#is this right to treat group as numeric? Summary doesn't provide AIC, BIC otherwise
```

##Longitudinal model
```{r, warning = FALSE, message = FALSE}
mydata_wide$Animal_TW_Clusters_2 <- as.numeric(scale(as.numeric(mydata_wide$Animal_TW_Clusters_2)))
mydata_wide$Animal_TW_Clusters_3 <- as.numeric(scale(as.numeric(mydata_wide$Animal_TW_Clusters_3)))
mydata_wide$Food_TW_Clusters_2 <- as.numeric(scale(as.numeric(mydata_wide$Food_TW_Clusters_2)))
mydata_wide$Food_TW_Clusters_3 <- as.numeric(scale(as.numeric(mydata_wide$Food_TW_Clusters_3)))
mydata_wide$IQ_vocraw_2 <- as.numeric(scale(as.numeric(mydata_wide$IQ_vocraw_2)))
mydata_wide$IQ_vocraw_3 <- as.numeric(scale(as.numeric(mydata_wide$IQ_vocraw_3)))

Long.mod <- ' 
            Semantic_1 =~ Animal_TW_Clusters_1 + Food_TW_Clusters_1 + IQ_vocraw_1
            Semantic_2 =~ Animal_TW_Clusters_2 + Food_TW_Clusters_2 + IQ_vocraw_2
            Semantic_3 =~ Animal_TW_Clusters_3 + Food_TW_Clusters_3 + IQ_vocraw_3

            ##correlated residuals across time
            Animal_TW_Clusters_1 ~~ Animal_TW_Clusters_2 + Animal_TW_Clusters_3
            Animal_TW_Clusters_2 ~~ Animal_TW_Clusters_3
            Food_TW_Clusters_1 ~~ Food_TW_Clusters_2 + Food_TW_Clusters_3
            Food_TW_Clusters_2 ~~ Food_TW_Clusters_3
            IQ_vocraw_1 ~~ IQ_vocraw_2 + IQ_vocraw_3
            IQ_vocraw_2 ~~ IQ_vocraw_3
'

fit.long <- cfa(Long.mod, data=mydata_wide, meanstructure = TRUE, std.lv = T, missing = "ML")
summary(fit.long, fit.measures = T)
semPaths(fit.long)
semPaths(fit.long, what = "est")
```


## 10. Test measurement invariance across time for your construct. Can you run growth models? If there is evidence of non-invariance, what seems to be the problem?  

My model is measurment invariant, suggesting that I'm measuring the same thing across time and allowing me to run growth models.
```{r}
#Step 1 -- configural model
config.fit <- fit.long
summary(config.fit, standardized = TRUE, fit.measures = T)
semPaths(config.fit)
semPaths(config.fit, what = "est")

#Step 2 -- weak model; constrain factor loadings to be the same across time
weak <- ' 
            ##define latent factors, constrain factor loadings
            Semantic_1 =~ L1*Animal_TW_Clusters_1 + L2*Food_TW_Clusters_1 + L3*IQ_vocraw_1
            Semantic_2 =~ L1*Animal_TW_Clusters_2 + L2*Food_TW_Clusters_2 + L3*IQ_vocraw_2
            Semantic_3 =~ L1*Animal_TW_Clusters_3 + L2*Food_TW_Clusters_3 + L3*IQ_vocraw_3

            ##free latent variables at later time points
            Semantic_2 ~~ NA*Semantic_2
            Semantic_3 ~~ NA*Semantic_3

            ##correlated residuals across time
            Animal_TW_Clusters_1 ~~ Animal_TW_Clusters_2 + Animal_TW_Clusters_3
            Animal_TW_Clusters_2 ~~ Animal_TW_Clusters_3
            Food_TW_Clusters_1 ~~ Food_TW_Clusters_2 + Food_TW_Clusters_3
            Food_TW_Clusters_2 ~~ Food_TW_Clusters_3
            IQ_vocraw_1 ~~ IQ_vocraw_2 + IQ_vocraw_3
            IQ_vocraw_2 ~~ IQ_vocraw_3
'

weak.fit <- cfa(weak, data=mydata_wide, meanstructure = TRUE, std.lv = T, missing = "ML")
summary(weak.fit, standardized = TRUE, fit.measures = T)
semPaths(weak.fit)
semPaths(weak.fit, what = "est")

#Compare models -- difference is not significant -- no evidence thus far of non-invariance
anova(config.fit, weak.fit)

#Also look at change in CFI
print(fitMeasures(weak.fit, "cfi") - fitMeasures(config.fit, "cfi")) < .01

#Step 3 -- strong model; constrain means/intercepts of indicators to be equal
strong <-  '
            ##define latent factors, constrain factor loadings
            Semantic_1 =~ L1*Animal_TW_Clusters_1 + L2*Food_TW_Clusters_1 + L3*IQ_vocraw_1
            Semantic_2 =~ L1*Animal_TW_Clusters_2 + L2*Food_TW_Clusters_2 + L3*IQ_vocraw_2
            Semantic_3 =~ L1*Animal_TW_Clusters_3 + L2*Food_TW_Clusters_3 + L3*IQ_vocraw_3

            ##free latent variables at later time points
            Semantic_2 ~~ NA*Semantic_2
            Semantic_3 ~~ NA*Semantic_3

            ##correlated residuals across time
            Animal_TW_Clusters_1 ~~ Animal_TW_Clusters_2 + Animal_TW_Clusters_3
            Animal_TW_Clusters_2 ~~ Animal_TW_Clusters_3
            Food_TW_Clusters_1 ~~ Food_TW_Clusters_2 + Food_TW_Clusters_3
            Food_TW_Clusters_2 ~~ Food_TW_Clusters_3
            IQ_vocraw_1 ~~ IQ_vocraw_2 + IQ_vocraw_3
            IQ_vocraw_2 ~~ IQ_vocraw_3

            ##constrain intercepts across time
            Animal_TW_Clusters_1 ~ A*1
            Food_TW_Clusters_1 ~   B*1
            IQ_vocraw_1 ~          C*1

            Animal_TW_Clusters_2 ~ A*1
            Food_TW_Clusters_2 ~   B*1
            IQ_vocraw_2 ~          C*1

            Animal_TW_Clusters_3 ~ A*1
            Food_TW_Clusters_3 ~   B*1
            IQ_vocraw_3 ~          C*1

            ##free latent means at later times
            Semantic_2 ~ NA*1
            Semantic_3 ~ NA*1
'

strong.fit <- cfa(strong, data=mydata_wide, meanstructure = TRUE, std.lv = T, missing = "ML")
summary(strong.fit, standardized = TRUE, fit.measures = T)
semPaths(strong.fit)
semPaths(strong.fit, what = "est")

#Compare models -- difference is not significant -- no evidence thus far of non-invariance
anova(weak.fit, strong.fit)

#Also look at change in CFI
#Change in CFI = .012, which is greater than .01 threshold but not by much
#On the whole, model appears to be measurement invariant
print(fitMeasures(strong.fit, "cfi") - fitMeasures(weak.fit, "cfi")) < .01
```

## 11. Fit a second order growth model. Compare and contrast the estimates with the normal latent growth model.  

Estimates are fairly similar, although not identical, using second and first-order growth models (see comb2 dataframe). However, as discussed in class, the second-order model is preferred because it allows us to test for measurment invariance and account for occasion-specific variance. Likewise, it hugely improves model fit (e.g., TLI .64 vs. .98).
```{r, warning = F, message = F}
#Second order growth model
second_order <- ' 
            ##define latent factors, constrain factor loadings
            Semantic_1 =~ NA*Animal_TW_Clusters_1 + L1*Animal_TW_Clusters_1 + L2*Food_TW_Clusters_1 + L3*IQ_vocraw_1
            Semantic_2 =~ NA*Animal_TW_Clusters_2 + L1*Animal_TW_Clusters_2 + L2*Food_TW_Clusters_2 + L3*IQ_vocraw_2
            Semantic_3 =~ NA*Animal_TW_Clusters_3 + L1*Animal_TW_Clusters_3 + L2*Food_TW_Clusters_3 + L3*IQ_vocraw_3

            ##correlated residuals across time
            Animal_TW_Clusters_1 ~~ Animal_TW_Clusters_2 + Animal_TW_Clusters_3
            Animal_TW_Clusters_2 ~~ Animal_TW_Clusters_3
            Food_TW_Clusters_1 ~~ Food_TW_Clusters_2 + Food_TW_Clusters_3
            Food_TW_Clusters_2 ~~ Food_TW_Clusters_3
            IQ_vocraw_1 ~~ IQ_vocraw_2 + IQ_vocraw_3
            IQ_vocraw_2 ~~ IQ_vocraw_3

            ##constrain intercepts across time
            Animal_TW_Clusters_1 ~ A*1
            Food_TW_Clusters_1 ~   B*1
            IQ_vocraw_1 ~          C*1

            Animal_TW_Clusters_2 ~ A*1
            Food_TW_Clusters_2 ~   B*1
            IQ_vocraw_2 ~          C*1

            Animal_TW_Clusters_3 ~ A*1
            Food_TW_Clusters_3 ~   B*1
            IQ_vocraw_3 ~          C*1

            ##latent variable intercepts
            Semantic_1 ~ 0*1
            Semantic_2 ~ 0*1
            Semantic_3 ~ 0*1

            
            ##CHOSING NOT TO IMPLEMENT EFFECT CODING TO FACILIATE COMPARISON OF ESTIMATES WITH NORMAL LATENT MODEL
            ##model constraints for effect coding
            ##loadings must average to 1
            ##L1 == 3 - L2 - L3
            ##means must average to 0
            ##A == 0 - B - C

            ##Define latent factors for slope and intercept
            i =~ 1*Semantic_1 + 1*Semantic_2 + 1*Semantic_3
            s =~ 0*Semantic_1 + 1*Semantic_2 + 2*Semantic_3
'

second_order.fit <- cfa(second_order, data=mydata_wide, meanstructure = TRUE, missing = "ML")
#"WARNING: some estimate lv variances are negative"
#Indicates that there's not much variance in the slope
#Tried playing around with constraints, then model failed to converge or got I the "not positive definite" message
#How bad are negative lv variances? Given they're only slightly negative, can the model still be trusted?
summary(second_order.fit, standardized = TRUE, fit.measures = T)
semPaths(second_order.fit)
semPaths(second_order.fit, what = "est")

#Normal latent growth model
first_order <- '
              i =~ 1*Animal_TW_Clusters_1 + 1*Food_TW_Clusters_1 + 1*IQ_vocraw_1 +
                   1*Animal_TW_Clusters_2 + 1*Food_TW_Clusters_2 + 1*IQ_vocraw_1 +
                   1*Animal_TW_Clusters_3 + 1*Food_TW_Clusters_3 + 1*IQ_vocraw_3
              s =~ 0*Animal_TW_Clusters_1 + 0*Food_TW_Clusters_1 + 0*IQ_vocraw_1 +
                   1*Animal_TW_Clusters_2 + 1*Food_TW_Clusters_2 + 1*IQ_vocraw_1 +
                   2*Animal_TW_Clusters_3 + 2*Food_TW_Clusters_3 + 2*IQ_vocraw_3
'

##Compare and contrast estimates with normal latent growth model
first_order.fit <- cfa(first_order, data=mydata_wide, meanstructure = TRUE, missing = "ML")
#"WARNING: some estimate lv variances are negative"
#Indicates that there's not much variance in the slope
#Tried playing around with constraints, then model failed to converge or got I the "not positive definite" message
#How bad are negative lv variances? Given they're only slightly negative, can the model still be trusted?
summary(first_order.fit, standardized = TRUE, fit.measures = T)
semPaths(first_order.fit)
semPaths(first_order.fit, what = "est")

##Grab estimates for normal and second-order models
long_mod <- as_tibble(parameterEstimates(first_order.fit)) %>%
  dplyr::select(1:4) %>%
  rename("Est_long" = "est") %>%
  unite(Var, lhs, op, rhs)

sec_mod <- as_tibble(parameterEstimates(second_order.fit)) %>%
  dplyr::select(c(1,2,3,5)) %>%
  rename("Est_second" = "est") %>%
  unite(Var, lhs, op, rhs)

##Create data frame to visualize estimates for normal and second order models side by side
comb <- full_join(long_mod, sec_mod, by= "Var") %>%
  mutate_at(c("Est_long", "Est_second"), funs(round(., 3)))
comb2 <- comb[17:35,]

##Evaluating fit
fitMeasures(first_order.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
fitMeasures(second_order.fit, c("tli", "cfi", "rmsea", "srmr", "chisq"))
```

## 12. Fit a series of multiple group models. Constrain some parameters and compare the fit.
```{r}
#TBC...
```

