---
title: "Week3_MLM"
author: "Zoë Hawks"
date: "9/24/2017"
output: 
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, include = FALSE}
#importing datasets
setwd("/Users/zashawks/Desktop/PNL/PKU/Verbal Fluency/")
mydata_wide <- read.csv("VerbalFluency_StrategicProcessing.csv", header=TRUE)
mydata_long <- read.csv("NJ_data_3.csv")
mydata_dob <- read.csv("IQ_VF_participants.csv")

setwd("/Users/zashawks/Desktop/Stats/Longitudinal/ALDA")
library(tidyverse)
library(tibble)
library(lubridate)
```

```{r setup2, include = FALSE}
#setting up dataframe
mydata_dob2 <- mydata_dob %>%
  select(IDNUMBER, GENDER, GROUP, L1dob, L1age, L1dot,
         L2dob, L2age, L2dot, L3dob, L3age, L3dot) %>%
  mutate_at(c(4, 6, 7, 9, 10, 12), as.character) %>%
  rename(ID2 = IDNUMBER, L1_dob = L1dob, L1_age = L1age, L1_dot = L1dot,
         L2_dob = L2dob, L2_age = L2age, L2_dot = L2dot, L3_dob = L3dob, L3_age = L3age, L3_dot = L3dot)

mydata_merged <- left_join(mydata_wide, mydata_dob2)

mydata_merged$L1_S_TotalCorrect <- as.numeric(mydata_merged$L1_S_TotalCorrect)
mydata_merged$L1_f_TotalCorrect <- as.numeric(mydata_merged$L1_f_TotalCorrect)
mydata_merged$L1_Pho_TotalCorrect <- (mydata_merged$L1_f_TotalCorrect +
                                           mydata_merged$L1_S_TotalCorrect)

mydata_merged$L2_S_TotalCorrect <- as.numeric(mydata_merged$L2_S_TotalCorrect)
mydata_merged$L2_f_TotalCorrect <- as.numeric(mydata_merged$L2_f_TotalCorrect)
mydata_merged$L2_Pho_TotalCorrect <- (mydata_merged$L2_f_TotalCorrect +
                                           mydata_merged$L2_S_TotalCorrect)

mydata_merged$L3_S_TotalCorrect <- as.numeric(mydata_merged$L3_S_TotalCorrect)
mydata_merged$L3_f_TotalCorrect <- as.numeric(mydata_merged$L3_f_TotalCorrect)
mydata_merged$L3_Pho_TotalCorrect <- (mydata_merged$L3_f_TotalCorrect +
                                           mydata_merged$L3_S_TotalCorrect)

mydata_merged$baselinePho <- mydata_merged$L1_Pho_TotalCorrect
wide_to_long2 <- mydata_merged %>%
  gather(-ID2, -GENDER, -GROUP, -baselinePho, key = "timepoint", value = "value") %>%
  separate(timepoint, into = c("Omit", "Timepoint", "Omit2", "Variable"), sep = c(1,2, 3)) %>%
  select(-Omit, -Omit2) %>%
  spread(key = Variable, value = value) %>%
  drop_na() %>%
  mutate(dob = mdy(dob), dot = mdy(dot)) 
wide_to_long2 <- wide_to_long2[1:200, ]

mydata_dob2$baselinedate <- mydata_dob2$L1_dot
wide_to_long3 <- mydata_dob2 %>%
  gather(-ID2, -GENDER, -GROUP, -baselinedate, key = "timepoint", value = "value") %>%
  separate(timepoint, into = c("Omit", "Timepoint", "Omit2", "Variable"), sep = c(1,2, 3)) %>%
  select(-Omit, -Omit2) %>%
  spread(key = Variable, value = value) %>%
  drop_na() %>%
  mutate(dob = mdy(dob), dot = mdy(dot), baselinedate = mdy(baselinedate)) 
  
wide_to_long_merged <- full_join(wide_to_long2, wide_to_long3)
wide_to_long_merged <- as_tibble(wide_to_long_merged)
wide_to_long_merged

#Converting date  
#Age
wide_to_long_merged$Age_days <- round(as.duration(wide_to_long_merged$dob %--%
                                                    wide_to_long_merged$dot)/ddays(1), 1)
wide_to_long_merged$Age_weeks <- round(as.duration(wide_to_long_merged$dob %--%
                                                     wide_to_long_merged$dot)/dweeks(1), 1)
wide_to_long_merged$Age_years <- round(as.duration(wide_to_long_merged$dob %--%
                                                     wide_to_long_merged$dot)/dyears(1), 1)
  
#Time in study
wide_to_long_merged$TIS_days <- round(as.duration(wide_to_long_merged$baselinedate %--%
                                                    wide_to_long_merged$dot)/ddays(1))
wide_to_long_merged$TIS_weeks <- round(as.duration(wide_to_long_merged$baselinedate %--%
                                                     wide_to_long_merged$dot)/dweeks(1))
wide_to_long_merged$TIS_years <- round(as.duration(wide_to_long_merged$baselinedate %--%
                                                     wide_to_long_merged$dot)/dyears(1))

#Adjust type
wide_to_long_merged$GENDER <- as.factor(wide_to_long_merged$GENDER)
wide_to_long_merged$GROUP <- as.factor(wide_to_long_merged$GROUP)
wide_to_long_merged$age <- as.numeric(wide_to_long_merged$age)
wide_to_long_merged$animal_TotalCorrect <- as.numeric(wide_to_long_merged$animal_TotalCorrect)
wide_to_long_merged$food_TotalCorrect <- as.numeric(wide_to_long_merged$food_TotalCorrect)
  
levels(wide_to_long_merged$GROUP)[levels(wide_to_long_merged$GROUP)==2] <- "Control"
levels(wide_to_long_merged$GROUP)[levels(wide_to_long_merged$GROUP)==1] <- "PKU"
  
wide_to_long_merged$Sem_TotalCorrect <- (wide_to_long_merged$animal_TotalCorrect +
                                           wide_to_long_merged$food_TotalCorrect)

wide_to_long_merged$age.centered <- wide_to_long_merged$age - mean(wide_to_long_merged$age, na.rm = T)
```

##Problem 1:  
Run a series of models using a time-invariant nominal covariate. a) where the covariate only predicts the intercept b) predicts both intercept and slope c) is rescaled eg centering. For all models, how does your model change from model to model. What is your final model?  
  
*Part A: Fixed effect estimates*  
`Intercept` = 40.57; mean of Controls at mean age (age.centered = 0)  
`Age.centered` = 2.05; increase in words correct/year for all participants  
`Group` = -1.4; difference in words correct between Control and PKU at mean age (age.centered = 0)  
`Pseudo-R2` = .38 (marginal; fixed) and .69 (conditional; fixed + random)  

*Part B: Fixed effect estimates*  
`Intercept` = 40.93; mean of Controls at mean age (age.centered = 0)    
`Age.centered` = 2.33; increase in words correct/year for Controls  
`Group` = -2.25; difference in words correct between Control and PKU age mean age (age.centered = 0)  
`Age.centered:GROUP` = -.77; difference in slope between Control and PKU  
`Pseudo-R2` = .38 (marginal; fixed) and .70 (conditional; fixed + random)  

*Part C: Fixed effect estimates*  
`Intercept` = 38.69; mean of PKU at mean age (age.centered = 0)  
`Age.centered` = 1.56; increase in words correct/year for PKU  
`Group` = 2.25; difference in words correct between PKU and Controls at mean age (age.centered = 0)  
`Age.centered:GROUP` = .77; difference in slope between PKU and Control  
`Pseudo-R2` = .38 (marginal; fixed) and .70 (conditional; fixed + random)  
  
**Likelihood ratio test suggests that simpler model, where covariate only predicts intercept, is preferred.**  
```{r Problem1, warning = FALSE}
#Model from HW #2
library(lme4)
library(MuMIn)
wide_to_long_merged$Timepoint <- as.factor(wide_to_long_merged$Timepoint)
lin.mlm <- lmer(Sem_TotalCorrect ~ age.centered + (age.centered | ID2), data = wide_to_long_merged)
summary(lin.mlm)
anova(lin.mlm)
r.squaredGLMM(lin.mlm)

#Part a: adding group, a time-invariant nominal covariate that only predicts the intercept
wide_to_long_merged$GROUP <- relevel(wide_to_long_merged$GROUP, ref = "Control")
lin.nom1 <- lmer(Sem_TotalCorrect ~ age.centered + GROUP + 
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.nom1)
anova(lin.nom1)
r.squaredGLMM(lin.nom1)

#Part b: adding group, a time-invariant nominal covariate the predicts intercept and slope
wide_to_long_merged$GROUP <- relevel(wide_to_long_merged$GROUP, ref = "Control")
lin.nom2 <- lmer(Sem_TotalCorrect ~ age.centered + GROUP + age.centered:GROUP +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.nom2)
anova(lin.nom2)
r.squaredGLMM(lin.nom2)

#Part c: rescaling nominal variable (i.e., changing dummy coding such that refernce group becomes PKU)
wide_to_long_merged$GROUP <- relevel(wide_to_long_merged$GROUP, ref = "PKU")
lin.nom3 <- lmer(Sem_TotalCorrect ~ age.centered + GROUP + age.centered:GROUP +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.nom3)
anova(lin.nom3)
r.squaredGLMM(lin.nom3)

#Likelihood ratio test
anova(lin.nom1, lin.nom2)
```
  
##Problem 2:  
  
*Part A: Fixed effect estimates*  
`Intercept` = 37.46; mean across all participants at means levels of age (i.e., age.centered = 0) and when baselinePho = 0  
`Age.centered` = 1.91; slope (increase in words correct/year) at when baselinePho = 0  
`baselinePho` = .13; slope (increase in words correct/unit of baselinePho) at mean age (age.centered = 0)  
`Pseudo-R2` = .39 (marginal; fixed) and .68 (conditional; fixed + random)  

*Part B: Fixed effect estimates*  
`Intercept` = 37.46; mean across all participants at mean age (age.centered = 0) and when baselinePho = 0  
`Age.centered` = 1.80; slope (increase in words correct/year) when baselinePho = 0  
`baselinePho` = .13; slope (increase in words correct/unit of baselinePho) at mean age (age.centered = 0)    
`Age.centered:baselinePho` = .006; extent to which relationship between age.centered and Sem_Total_Correct changes at different levels of baselinePho (change is minimal)  
`Pseudo-R2` = .39 (marginal; fixed) and .68 (conditional; fixed + random)  

*Part C: Fixed effect estimates*  
`Intercept` = 39.94; mean across all participants at means levels of age and baselinePho (i.e., age.centered and baselinePho.centered = 0)  
`Age.centered` = 1.90; slope (increase in words correct/year) at mean levels of baselinePho (baselinePho.centered = 0)  
`baselinePho` = .13; slope (increase in words correct/unit of baselinePho) at mean age (age.centered = 0)  
`Age.centered:baselinePho` = .006; extent to which relationship between age.centered and Sem_Total_Correct changes at different levels of baselinePho (change is minimal; this does not change as a function of centering)  
`Pseudo-R2` = .39 (marginal; fixed) and .68 (conditional; fixed + random)  
  
**Likelihood ratio test suggests that simpler model, where covariate only predicts intercept, is preferred.**  
```{r Problem2, warning = FALSE}
#Part a: adding baselinePho, a time-invariant continuous covariate that only predicts the intercept
lin.cont1 <- lmer(Sem_TotalCorrect ~ age.centered + baselinePho + 
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.cont1)
anova(lin.cont1)
r.squaredGLMM(lin.cont1)

#Part b: adding group, a time-invariant nominal covariate the predicts intercept and slope
lin.cont2 <- lmer(Sem_TotalCorrect ~ age.centered + baselinePho + age.centered:baselinePho +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.cont2)
anova(lin.cont2)
r.squaredGLMM(lin.cont2)

#Part c: rescaling nominal variable (i.e., centering baselinePho)
wide_to_long_merged$baselinePho.centered <- wide_to_long_merged$baselinePho - 
  mean(wide_to_long_merged$baselinePho, na.rm = T)
lin.cont3 <- lmer(Sem_TotalCorrect ~ age.centered + baselinePho.centered + age.centered:baselinePho.centered +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.cont3)
anova(lin.cont3)
r.squaredGLMM(lin.cont3)

#Likelihood ratio test
anova(lin.cont1, lin.cont2)
```

##Problem 3:  
Graph both of your final models for the continuous and nominal models above.
```{r Problem3, warning = FALSE}
#Graphing nominal
library(sjPlot)
sjp.lmer(lin.nom1, type = "pred.fe", var = c("age.centered", "GROUP"), facet = FALSE, show.scatter = FALSE)
sjp.int(lin.nom2, swap.pred = T)

#Graphing continuous
sjp.lmer(lin.cont1, type = "pred", var = c("age.centered"), show.scatter = FALSE, show.ci = TRUE)
sjp.int(lin.cont2, swap.pred = T, mdrt.values = "meansd")
```

##Problem 4:  
Calculate confidence intervals around your estimates for your final models  
```{r Problem4, warning = FALSE}
#Confidence intervals around nominal model
lin.nom.ci <- confint(lin.nom1, level = .95, oldNames = F, method = "boot", nsim = 100)
broom::tidy(lin.nom.ci)

#Confidence intervals around continuous model
lin.cont.ci <- confint.merMod(lin.cont1, level = .95, oldNames = F, method = "boot", nsim = 100)
broom::tidy(lin.cont.ci)
```

##Problem 5:  
Include both types of covariates in a single model. How does your interpretation of parameters change?  
  
*Fixed effect estimates:*  
`Intercept` = 40.94; mean of Controls at mean levels of age and baselinePho (i.e., age.centered and baselinePho.centered = 0)  
`Age.centered` = 2.25; slope of Controls (increase in words correct/year) at mean levels of baselinePho (i.e., baselinePho.centered = 0)  
`baselinePho.centered` = .10; slope of Controls (increase in words correct/unit of baselinePho) at mean levels of age (i.e., age.centered = 0)  
`GROUP` = -2.73; difference in words correct between Control and PKU at mean levels of age and baselinePho (i.e., when age.centered and baselinePho.centered = 0)  
`age.centered:baselinePho.centered` = -.02; extent to which relationship between age.centered and Sem_TotalCorrect changes at different levels of baselinePho.centered, when group = Controls  
`age.centered:GROUP` = -.63; extent to which relationship between age.centered and Sem_TotalCorrect changes at different levels of GROUP, when baselinePho.centered = 0  
`baselinePho.centered:GROUP` = -.05; extent to which relationship between baselinePho.centered and Sem_TotalCorrect changes at different levels of GROUP, when age.centered = 0  
`age.centered:baselinePho.centered:GROUP` = .09; extent to which the interaction between age.centered and baselinePho.centered changes at different levels of GROUP  
`Pseudo-R2` = .39 (marginal; fixed) and .70 (conditional; fixed + random)  
```{r Problem 5}
wide_to_long_merged$GROUP <- relevel(wide_to_long_merged$GROUP, ref = "Control")
lin.comb <- lmer(Sem_TotalCorrect ~ age.centered*baselinePho.centered*GROUP +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.comb)
anova(lin.comb)
r.squaredGLMM(lin.comb)
```
