---
title: "Week3_MLM"
author: "Zoë Hawks"
date: "9/24/2017"
output: 
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, include = FALSE}
#importing datasets
setwd("/Users/zashawks/Desktop/PNL/PKU/Verbal Fluency/")
mydata_wide <- read.csv("VerbalFluency_StrategicProcessing.csv", header=TRUE)
mydata_long <- read.csv("NJ_data_3.csv")
mydata_dob <- read.csv("IQ_VF_participants.csv")

setwd("/Users/zashawks/Desktop/Stats/Longitudinal/ALDA")
library(tidyverse)
library(tibble)
library(lubridate)
```

```{r setup2, include = FALSE}
#setting up dataframe
mydata_dob2 <- mydata_dob %>%
  select(IDNUMBER, GENDER, GROUP, L1dob, L1age, L1dot,
         L2dob, L2age, L2dot, L3dob, L3age, L3dot) %>%
  mutate_at(c(4, 6, 7, 9, 10, 12), as.character) %>%
  rename(ID2 = IDNUMBER, L1_dob = L1dob, L1_age = L1age, L1_dot = L1dot,
         L2_dob = L2dob, L2_age = L2age, L2_dot = L2dot, L3_dob = L3dob, L3_age = L3age, L3_dot = L3dot)

mydata_merged <- left_join(mydata_wide, mydata_dob2)

mydata_merged$L1_S_TotalCorrect <- as.numeric(mydata_merged$L1_S_TotalCorrect)
mydata_merged$L1_f_TotalCorrect <- as.numeric(mydata_merged$L1_f_TotalCorrect)
mydata_merged$L1_Pho_TotalCorrect <- (mydata_merged$L1_f_TotalCorrect +
                                           mydata_merged$L1_S_TotalCorrect)

mydata_merged$L2_S_TotalCorrect <- as.numeric(mydata_merged$L2_S_TotalCorrect)
mydata_merged$L2_f_TotalCorrect <- as.numeric(mydata_merged$L2_f_TotalCorrect)
mydata_merged$L2_Pho_TotalCorrect <- (mydata_merged$L2_f_TotalCorrect +
                                           mydata_merged$L2_S_TotalCorrect)

mydata_merged$L3_S_TotalCorrect <- as.numeric(mydata_merged$L3_S_TotalCorrect)
mydata_merged$L3_f_TotalCorrect <- as.numeric(mydata_merged$L3_f_TotalCorrect)
mydata_merged$L3_Pho_TotalCorrect <- (mydata_merged$L3_f_TotalCorrect +
                                           mydata_merged$L3_S_TotalCorrect)

mydata_merged$baselinePho <- mydata_merged$L1_Pho_TotalCorrect
wide_to_long2 <- mydata_merged %>%
  gather(-ID2, -GENDER, -GROUP, -baselinePho, key = "timepoint", value = "value") %>%
  separate(timepoint, into = c("Omit", "Timepoint", "Omit2", "Variable"), sep = c(1,2, 3)) %>%
  select(-Omit, -Omit2) %>%
  spread(key = Variable, value = value) %>%
  drop_na() %>%
  mutate(dob = mdy(dob), dot = mdy(dot)) 
wide_to_long2 <- wide_to_long2[1:200, ]

mydata_dob2$baselinedate <- mydata_dob2$L1_dot
wide_to_long3 <- mydata_dob2 %>%
  gather(-ID2, -GENDER, -GROUP, -baselinedate, key = "timepoint", value = "value") %>%
  separate(timepoint, into = c("Omit", "Timepoint", "Omit2", "Variable"), sep = c(1,2, 3)) %>%
  select(-Omit, -Omit2) %>%
  spread(key = Variable, value = value) %>%
  drop_na() %>%
  mutate(dob = mdy(dob), dot = mdy(dot), baselinedate = mdy(baselinedate)) 
  
wide_to_long_merged <- full_join(wide_to_long2, wide_to_long3)
wide_to_long_merged <- as_tibble(wide_to_long_merged)
wide_to_long_merged

#Converting date  
#Age
wide_to_long_merged$Age_days <- round(as.duration(wide_to_long_merged$dob %--%
                                                    wide_to_long_merged$dot)/ddays(1), 1)
wide_to_long_merged$Age_weeks <- round(as.duration(wide_to_long_merged$dob %--%
                                                     wide_to_long_merged$dot)/dweeks(1), 1)
wide_to_long_merged$Age_years <- round(as.duration(wide_to_long_merged$dob %--%
                                                     wide_to_long_merged$dot)/dyears(1), 1)
  
#Time in study
wide_to_long_merged$TIS_days <- round(as.duration(wide_to_long_merged$baselinedate %--%
                                                    wide_to_long_merged$dot)/ddays(1))
wide_to_long_merged$TIS_weeks <- round(as.duration(wide_to_long_merged$baselinedate %--%
                                                     wide_to_long_merged$dot)/dweeks(1))
wide_to_long_merged$TIS_years <- round(as.duration(wide_to_long_merged$baselinedate %--%
                                                     wide_to_long_merged$dot)/dyears(1))

#Adjust type
wide_to_long_merged$GENDER <- as.factor(wide_to_long_merged$GENDER)
wide_to_long_merged$GROUP <- as.factor(wide_to_long_merged$GROUP)
wide_to_long_merged$age <- as.numeric(wide_to_long_merged$age)
wide_to_long_merged$animal_TotalCorrect <- as.numeric(wide_to_long_merged$animal_TotalCorrect)
wide_to_long_merged$food_TotalCorrect <- as.numeric(wide_to_long_merged$food_TotalCorrect)
  
levels(wide_to_long_merged$GROUP)[levels(wide_to_long_merged$GROUP)==2] <- "Control"
levels(wide_to_long_merged$GROUP)[levels(wide_to_long_merged$GROUP)==1] <- "PKU"
  
wide_to_long_merged$Sem_TotalCorrect <- (wide_to_long_merged$animal_TotalCorrect +
                                           wide_to_long_merged$food_TotalCorrect)

wide_to_long_merged$age.centered <- wide_to_long_merged$age - mean(wide_to_long_merged$age, na.rm = T)
```

##Problem #1:  
Run a series of models using a time-invariant nominal covariate. a) where the covariate only predicts the intercept b) predicts both intercept and slope c) is rescaled eg centering. For all models, how does your model change from model to model. What is your final model?
```{r Problem1, warning = FALSE}
#Model from HW #2
library(lme4)
library(MuMIn)
wide_to_long_merged$Timepoint <- as.factor(wide_to_long_merged$Timepoint)
lin.mlm <- lmer(Sem_TotalCorrect ~ age.centered + (age.centered | ID2), data = wide_to_long_merged)
summary(lin.mlm)
anova(lin.mlm)
r.squaredGLMM(lin.mlm)

#Part a: adding group, a time-invariant nominal covariate that only predicts the intercept
wide_to_long_merged$GROUP <- relevel(wide_to_long_merged$GROUP, ref = "Control")
lin.nom1 <- lmer(Sem_TotalCorrect ~ age.centered + GROUP + 
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.nom1)
anova(lin.nom1)
r.squaredGLMM(lin.nom1)

#Part b: adding group, a time-invariant nominal covariate the predicts intercept and slope
wide_to_long_merged$GROUP <- relevel(wide_to_long_merged$GROUP, ref = "Control")
lin.nom2 <- lmer(Sem_TotalCorrect ~ age.centered + GROUP + age.centered:GROUP +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.nom2)
anova(lin.nom2)
r.squaredGLMM(lin.nom2)

#Part c: rescaling nominal variable (i.e., changing dummy coding such that refernce group becomes PKU)
wide_to_long_merged$GROUP <- relevel(wide_to_long_merged$GROUP, ref = "PKU")
lin.nom3 <- lmer(Sem_TotalCorrect ~ age.centered + GROUP + age.centered:GROUP +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.nom3)
anova(lin.nom3)
r.squaredGLMM(lin.nom3)

#Likelihood ratio test
anova(lin.nom1, lin.nom2)
```
*Part A:*  
Fixed effect intercept = 40.57; mean of Controls  
Age.centered = 2.05; increase in words correct/year for all participants (cov. only predicts intercept)  
Group = -1.4; difference in words correct between Control and PKU when age.centered = 0  
Pseudo-R2 = .38 (marginal; fixed) and .69 (conditional; fixed + random)  

*Part B:*  
Fixed effect intercept = 40.93; mean of Controls  
Age.centered = 2.33; increase in words correct/year for Controls  
Group = -2.25; difference in words correct between Control and PKU when age.centered = 0  
Age.centered:GROUP = -.77; difference in slope between Control and PKU  
Pseudo-R2 = .38 (marginal; fixed) and .70 (conditional; fixed + random)  

*Part C:*  
Fixed effect intercept = 38.69; mean of PKU  
Age.centered = 1.56; increase in words correct/year for PKU  
Group = 2.25; difference in words correct between PKU and Controls when age.centered = 0  
Age.centered:GROUP = .77; difference in slope between PKU and Control  
Pseudo-R2 = .38 (marginal; fixed) and .70 (conditional; fixed + random)  
  
**Likelihood ratio test suggests that simpler model, where covariate only predicts intercept, is preferred. However, age:group interaction term is theoretically important, so choosing lin.nom2 as the final model for Problem 3.**  
  
##Problem 2:  
```{r Problem2, warning = FALSE}
#Part a: adding baselinePho, a time-invariant continuous covariate that only predicts the intercept
lin.cont1 <- lmer(Sem_TotalCorrect ~ age.centered + baselinePho + 
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.cont1)
anova(lin.cont1)
r.squaredGLMM(lin.cont1)

#Part b: adding group, a time-invariant nominal covariate the predicts intercept and slope
lin.cont2 <- lmer(Sem_TotalCorrect ~ age.centered + baselinePho + age.centered:baselinePho +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.cont2)
anova(lin.cont2)
r.squaredGLMM(lin.cont2)

#Part c: rescaling nominal variable (i.e., centering baselinePho)
wide_to_long_merged$baselinePho.centered <- wide_to_long_merged$baselinePho - 
  mean(wide_to_long_merged$baselinePho, na.rm = T)
lin.cont3 <- lmer(Sem_TotalCorrect ~ age.centered + baselinePho.centered + age.centered:baselinePho.centered +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.cont3)
anova(lin.cont3)
r.squaredGLMM(lin.cont3)

#Likelihood ratio test
anova(lin.cont1, lin.cont2)
```
*Part A:*  
Fixed effect intercept = 37.46; mean when age.centered and baselinePho = 0  
Age.centered = 1.91; slope when baselinePho = 0  
baselinePho = .13; slope when age.centered = 0  
Pseudo-R2 = .39 (marginal; fixed) and .68 (conditional; fixed + random)  

*Part B:*  
Fixed effect intercept = 37.46; mean when age.centered and baselinePho = 0  
Age.centered = 1.80; slope when baselinePho = 0  
baselinePho = .13; slope when age.centered = 0    
Age.centered:baselinePho = .006; extent to which relationship between age.centered and Sem_Total_Correct changes at different levels of baselinePho (change is minimal)  
Pseudo-R2 = .39 (marginal; fixed) and .68 (conditional; fixed + random)  

*Part C:*  
Fixed effect intercept = 39.94; mean when age.centered and baselinePho (now mean centered) = 0  
Age.centered = 1.90; slope when baselinePho = 0  
baselinePho = .13; slope when age.centered = 0  
Age.centered:baselinePho = .006; extent to which relationship between age.centered and Sem_Total_Correct changes at different levels of baselinePho (change is minimal; does not change as a function of centering)  
Pseudo-R2 = .39 (marginal; fixed) and .68 (conditional; fixed + random)  
  
**Likelihood ratio test suggests that simpler model, where covariate only predicts intercept, is preferred. However, age:baselinePhe interaction term is theoretically important, so choosing lin.cont2 as the final model for Problem 3.**  

##Problem 3:  
Graph both of your final models for the continuous and nominal models above.
```{r Problem3, warning = FALSE}
#Graphing nominal
library(sjPlot)
sjp.int(lin.nom2, swap.pred = T)

#Graphing continuous
sjp.int(lin.cont2, swap.pred = T, mdrt.values = "meansd", plevel = 1)
```

##Problem 4:  
Calculate confidence intervals around your estimates for your final models  
```{r Problem4, warning = FALSE}
#Confidence intervals around nominal model
lin.nom.ci <- confint(lin.nom2, level = .95, oldNames = F)
broom::tidy(lin.nom.ci)

#Confidence intervals around continuous model
lin.cont.ci <- confint.merMod(lin.cont2, level = .95, oldNames = F)
broom::tidy(lin.cont.ci)
```

##Problem 5:  
Include both types of covariates in a single model. How does your interpretation of parameters change?
```{r Problem 5}
wide_to_long_merged$GROUP <- relevel(wide_to_long_merged$GROUP, ref = "Control")
lin.comb <- lmer(Sem_TotalCorrect ~ age.centered + baselinePho.centered + GROUP + age.centered:GROUP +
                   (age.centered | ID2), data = wide_to_long_merged)
summary(lin.comb)
anova(lin.comb)
r.squaredGLMM(lin.comb)
```
Fixed effect intercept = 40.74; mean when age.centered = 0, baselinePho.centered = 0, and GROUP = Control  
Age.centered = 2.22; slope when baselinePho.centered = 0 and GROUP = Control  
baselinePho.centered = .09; slope age.centered = 0 and GROUP = Control  
GROUP = -1.88; difference in words correct between Control and PKU when age.centered and baselinePho.centered = 0  
age.centered:GROUP = difference in slope between Control and PKU as a function of age.centered, when baselinePho.centered = 0  
Pseudo-R2 = .39 (marginal; fixed) and .70 (conditional; fixed + random)  
